Structural Variability

### 2016-04-11 INFORMATION/paper.tex
cambios 11/04/2016

\section{Conclusion}
Not much of a paper, but it's a start.

>>>>

{\bf LF-ENM model of mutant proteins:}

To simulate mutants of each reference protein and thus to generate datasets of theoretical proteins, we used the ``Linearly Forced Elastic Network Model'' (LF - ENM). This model predicts the effect of a single mutation adding a linear perturbative term to the reference potential:

Agregar formula

where $f$ is a column vector with $3N$ elements that models the mutation. The equilibrium structure of the mutant $r^{0}_{mut}$ is the value of $r$ that minimizes $V_{mut}$. Using Eqs. (1) and (2) we find the structural variation due to the mutation:

Agregar formula

This equation shows that the structural perturbation introduced by a mutation is related to the mutation and to the network of oscillators, via $K^{1}$. We should note here that $K^{1}$ is actually the pseudo inverse, because $K$ has six zero eigenvalues, corresponding to translations and rotations, so that it is not invertible.

{\bf Multiple-sites mutants: }
In order to simulate adequately the experimental data, we did not simulated proteins with a single mutation, we did simulate proteins with multiple mutations. To do this, we considered additive mutations by the assumption that $K^{mut}$ \cong $K^{wt}$:

\begin{equation}
dr^{tot} = dr^{mut1}_{wt} + dr^{mut2}_{wt} + ... + dr^{mutNmut}_{wt} = K^{-1}_{wt} \times (fmut1+fmut2+...+fmutNmut) 
\end{equation}

Where $dr^{tot}$ is the total structural variation due the M mutations, dr^{mutm}_{wt} is the structural variation produced by the mutation $m$considering $K^{wt}$, and fmutn is the vector of force of $n$.

\section{Results and discussion}

\section{Conclusion}
